%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
  {Ginkgo Bioworks} % Job title
  {Software Engineer} % Organization
  {Boston, MA} % Location
  {Aug 2020 - Present} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Worked as an individual contributor on the Solution Engineering team identifying gaps in core software, proposing and designing technical solutions, driving cross-team initiatives in an Agile environment, and unblocking high-impact projects.}
    \end{cvitems}
  }

\cventry
  {Weissman Lab} % Job title
  {Research Assistant} % Organization
  {Cambridge, MA} % Location
  {Dec 2020 - Jun 2022} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Studied cancer evolution via synthetic lineage reconstruction using a CRISPR-enabled lineage tracer in a lung cancer mouse model.}
      \item {Developed a tool to preprocess single cell metabolic labeling data to quantify RNA splicing kinetics.}
      \item {Developed new approahces of integrating multi-modal single-cell measurements (gene expression, lineage, spatial)}
    \end{cvitems}
  }

  \cventry
    {Ginkgo Bioworks} % Job title
    {Software Solution Engineering Intern} % Organization
    {Boston, MA} % Location
    {Jun 2020 - Aug 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked on migrating Ginkgo's mass spectrometry data pipeline to AWS and Airflow.}
        \item {Was responsible for the full development cycle of the project---from conceptualization, making architectural and design decisions to implementation, validation, and release.}
      \end{cvitems}
    }

%---------------------------------------------------------
\cventry
  {Pachter Lab} % Job title
  {Undergraduate Researcher} % Organization
  {Pasadena, CA} % Location
  {Sept 2019 - Jun 2020} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Worked with \textbf{\href{https://sinabooeshaghi.com/}{Sina Booeshaghi}} and \textbf{\href{https://pachterlab.github.io/biography.html}{Prof Lior Pachter}} on single-cell RNA-seq projects.}
      \item {Developed a friendly wrapper around a popular scRNA-seq pre-processing pipeline (kb-python).}
      \item {Developed a user interface for the open-source fraction collector (Colosseum) using PyQt5 and later as a web application with React.js.}
    \end{cvitems}
  }

%---------------------------------------------------------
  \cventry
    {Ginkgo Bioworks} % Job title
    {Software Engineering Intern} % Organization
    {Boston, MA} % Location
    {Jun. 2019 - Sept 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Improved Ginkgo's in-house data analysis pipeline and various backend services.}
        \item {Worked with other software engineers in an Agile environment to deliver stable, scalable and tested products.}
      \end{cvitems}
    }

%---------------------------------------------------------
\cventry
  {Sternberg Lab} % Job title
  {Undergraduate Researcher} % Organization
  {Pasadena, CA} % Location
  {Jan 2017 - Jun 2019} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Worked with \textbf{\href{https://dangeles.github.io/}{David Angeles PhD.}} and \textbf{\href{http://wormlab.caltech.edu/LabMembers/Paul}{Prof Paul W. Sternberg}} on projects involving the model organism C. elegans.}
      \item {Developed an automatic, complete RNA-seq pipeline for nematodes (Alaska).}
    \end{cvitems}
  }

\end{cventries}
